Miniproject - Analytic Number Theory

### 2021-12-19 Analytic number theory/submission.tex
Add proof that sum_p f(p)/p is negative to ANT

@@

    Wolfram Alpha \cite{wolfram_alpha} can give an explicit value to this sum, using the digamma function $\psi$. Namely

@@

        \sum_{x \in (\Z/4\Z)^\units} f(n) n^{-1} = \frac 1 4 (\psi(\frac 7 4) - \psi(\frac 5 4))

@@

    which seems to be $\frac 1 4$.

@@

        \sum_p \frac {f(p)} {p^s} = \log( L(f, s) ) + O( \zeta(2\Re(s)) )

@@

    In particular, we see that

@@

    exists.

@@

    By Taylor series expansion, see that

@@

        \log(1 - x) = -x + O(|x|^2)

@@

        \log( L(f, s) ) =& \log\Bigl( \prod_p \sum_{k \geq 0} \frac {f(p^k)} {p^{ks}} \Bigr) = \log\Bigl( \prod_p \frac 1 {1 - f(p)/p^s} \Bigr) \\

@@

        = & \sum_p \frac {f(p)} {p^s} + O\Bigl( \underbrace{\sum_p \frac {f(p)} {p^{2\Re(s)}}}_{\leq \zeta(2\Re(s))} \Bigr) = \sum_p \frac {f(p)} {p^s} + O(\zeta(2\Re(s)))

@@

>>>>

    \label{ex:l_series_mod_4}

@@

    Wolfram Alpha \cite{wolfram_alpha} can give an explicit value to this sum. Namely

@@

        \sum_{n \geq 1} f(n) n^{-1} = \frac 2 3 + \frac 1 3 + \frac \pi 4 - 1 = \frac \pi 4

@@

@@

        \sum_p \frac {f(p)} {p^s} = \log( L(s, f) ) + O( \zeta(2\Re(s)) )

@@

    and so

@@

    exists. Furthermore, this value is negative.

@@

    By Taylor series expansion, see

@@

        \log(1 - x) = -x + O(x^2)

@@

        \log( L(s, f) ) =& \log\Bigl( \prod_p \sum_{k \geq 0} \frac {f(p^k)} {p^{ks}} \Bigr) = \log\Bigl( \prod_p \frac 1 {1 - f(p)/p^s} \Bigr) \\

@@

        = & \sum_p \frac {f(p)} {p^s} + O\Bigl( \underbrace{\sum_p \frac {f(p)^2} {p^{2\Re(s)}}}_{\leq \zeta(2\Re(s))} \Bigr) = \sum_p \frac {f(p)} {p^s} + O(\zeta(2\Re(s)))

@@

    Note further that for $|x| \leq \frac 1 2$
        \Bigl| \log(1 - x) + x + \frac {x^2} 2 \Bigr| \leq \Bigl| \frac {2x^3} 3 \Bigr|
    as by Taylor series expansion, find
        \log(1 - x) = -\sum_{n \geq 1} \frac {x^n} {n}
    Thus
        \Bigl| \log(L(s, f)) - \sum_p \frac {f(p)} {p^s} - \frac 1 2 \sum_p \frac {f(p)^2} {p^{2s}} \Bigr| \leq \frac 2 3 \sum_p \Bigl| \frac {f(p)^3} {p^{3s}} \Bigr|
    and since
        \frac 2 3 \sum_p \Bigl| \frac {f(p)^3} {p^3} \Bigr| \leq \frac 2 3 \sum_{n \geq 2} \frac 1 {n^3} = \frac 2 3 (\zeta(3) - 1) < \frac 1 5
    we see that
        \sum_p \frac {f(p)} p < \frac 1 5 - \underbrace{\frac 1 2 \sum_p \frac {f(p)^2} {p^2}}_{\geq 0} + \underbrace{\log(L(1, f))}_{\leq -1/5} \leq 0
    is negative.
    Here I used that $\zeta(3) \leq 13/10$ and $L(1, f) \leq \exp(-1/5)$, both of which can be considered generally known (see e.g. the previous example and \cite{wolfram_alpha}) and can be easily checked using a computer.
